Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/evaluation.tex

\begin{figure}[t]
\centering
\begin{minipage}{\linewidth}
\includegraphics[width=\linewidth]{coverage.pdf}
\end{minipage}
\begin{minipage}{\linewidth}
\includegraphics[width=\linewidth]{distrib.pdf}
\end{minipage}
% \vspace{-8ex}
\caption{Results of our coverage testing and the distribution of test
  outcomes. Our random search successfully finds witnesses for 83\% of
  the programs in under one second, improving slightly to 87\% in under
  10 seconds. In both datasets we detect actual type errors about 82\%
  of the time, unbound variables or constructors 3-4\% of the time, and
  diverging loops 2-3\% of the time. For the remaining 11-12\% of the
  programs we are unable to provide any useful feedback.  }
\label{fig:results-witness}
\end{figure}

@@

\paragraph{Jump Compression}
%
A jump compressed trace is one whose edges are limited to forward
or backward jumps. (The sizes of these traces is equal to the jump
metric below.)
%
In our experience, jump compression abstracts many details of the
computation that are often uninteresting or irrelevant to the
explanation, or at any rate, easily summarized as call-return
pairs.
%
Note that jump compressed traces are not quite the same as
stack-traces as they show \emph{all} function calls, including
those that returned successfully.
%
For example, the display on the right in Figure~\ref{fig:factorial} shows
a jump-compressed trace, of size 4. The full trace for
the same example has size 19.

>>>>

\begin{figure}[t]
\centering
\begin{minipage}{\linewidth}
\includegraphics[width=\linewidth]{coverage.pdf}
\end{minipage}
\begin{minipage}{\linewidth}
\includegraphics[width=\linewidth]{distrib.pdf}
\end{minipage}
% \vspace{-8ex}
\caption{Results of our coverage testing and the distribution of test
  % WRW notes that the pie chart does not print on standard department
  % printer, and is emailing a photo as proof. Possible solution:
  % convert PDF -> PNG and include PNG? 
  outcomes. Our random search successfully finds witnesses for 83\% of
  the programs in under one second, improving slightly to 87\% in under
  10 seconds. In both datasets we detect actual type errors about 82\%
  of the time, unbound variables or constructors 3-4\% of the time, and
  diverging loops 2-3\% of the time. For the remaining 11-12\% of the
  programs we are unable to provide any useful feedback.  }
\label{fig:results-witness}
\end{figure}

@@

\paragraph{Jump Compression}
%
A \emph{jump compressed} trace is one whose edges are limited to forward
or backward jumps. (The sizes of these traces is equal to the jump
metric below.)
%
In our experience, jump compression abstracts many details of the
computation that are often uninteresting or irrelevant to the
explanation, or at any rate, easily summarized as call-return
pairs.
% WRW: Say more here. This is critical to your evaluatino and to your
% conclusion (e.g., where we say that jump-compressed traces hide boring
% details). Why are these details boring and others relevant? Do the
% boring ones contain less information somehow? 
%
Note that jump compressed traces are not quite the same as
stack-traces as they show \emph{all} function calls, including
those that returned successfully.
%
For example, the display on the right in Figure~\ref{fig:factorial} shows
a jump-compressed trace, of size 4. The full trace for
the same example has size 19.
